---
title: 'STAT/CSSS 503: Assignment 4'
author: Jeffrey Arnold
bibliography: assignment4.bib
output:
  html_document:
    toc: false
    number_sections: true
  pdf_document:
    toc: false
    number_sections: true    
---

```{r include=FALSE}
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE)
```


# Instructions {-}

This repository contains the assignment instructions.
Submitted solutions will use a **separate** repository.

1. Fork [UW-CSSS-503/assignment-2017-4-submissions](https://github.com/UW-CSSS-503/assignment-2017-3-submissions) repository to your account.
2. Edit the file `assignment-4-solutions.Rmd` with your solutions to the problems.
3. Submit a pull request to have it graded. Include either or both a HTML and PDF file.

This assignment will require the following R packages:
```{r, message=FALSE}
library("AER")
```

**In Progress**

# Bailey 8.2

Complete Chapter 8, Exercise 2 in @Bailey2016a

# Bailey 8.5

Complete Chapter 8, Exercise 5 in @Bailey2016a

# Bailey 11.3

Complete Chapter 11, Exercise 3 in @Bailey2016a

# Bailey 11.4

Complete Chapter 11, Exercise 4 in @Bailey2016a

# Bailey 13.3

Complete Chapter 13, Exercise 3 in @Bailey2016a

# Bailey 15.1

Complete Chapter 15, Exercise 1 in @Bailey2016a


# References {-}
